Graph Learning from Binomial Signals

### 2022-05-27 Documents/paper/draft.Rmd
minor changes on the draft

Dong et al. propose a modified factor analysis model in @dong2016learning for learning a valid graph laplacian. The model proposed is given by 
$$x = \chi h + \mu_x + \epsilon$$
where $h \sim \mathcal{N}(0, \Lambda^{\dagger})$ is the latent variable,$\Lambda$ is the eigenvalue matrix of $L$, and  $\mu_x \in \mathbb{R}^N$ mean of $x$. The noise term $\epsilon$ is assumed to follow a multivariate Gaussian distribution with mean zero and covariance $\sigma_\epsilon^2I_N$. The key difference from traditional factor analysis is the choice of $\chi$ as a valid eigenvector matrix for a graph laplacian. Finding a maximum apriori estimate of $h$ reduces to solving the optimization problem

@@

<hr />
\begin{align*}
&\textbf{Algorithm 1: Binary Signal Graph Learning} \\
&1) \textbf{ Input: } \text{ Input a signal on a graph} \mathbf{Y}.\\
&2) \textbf{ Output: } \text{ Output an estimated } \mathbf{A}.\\
&3) \textbf{ Initialization: } h_{i,0} \sim \mathcal{N}(0,1) \text{ for } i = 1,\ldots, N \\
&4) \textbf{ for } t = 1, \ldots, iter:\\
&5) \textbf{ Update } \mathbf{A} \textbf{ given } h:\\
&6) \,\,\,\, \textit{ Fix }  h \textit{ in Optimization Program and solve } \mathbf{A} \\
&7) \textbf{        Update } h \textbf{ given } \mathbf{A}:\\
&8) \,\,\,\, \textit{ Fix } \mathbf{A} \text{ in Optimization Program and solve h} \\
&9) \textbf{ end for }
\end{align*}
<hr />

@@

his work is supported by Research, Scholarship, and Creative Activity (RSCA) Award 2021-2022 through Chico State Enterprises. Thank you to Dr. Robin Donatello, Ph.D., for approving this work for Data Science Capstone Project

@@

>>>>

Dong et al. propose a modified factor analysis model in @dong2016learning for learning a valid graph laplacian. The model proposed is given by 
$$x = \chi h + \mu_x + \epsilon$$
where $h \sim \mathcal{N}(0, \Lambda^{\dagger})$ is the latent variable,$\Lambda$ is the eigenvalue matrix of $L$, and  $\mu_x \in \mathbb{R}^N$ mean of $x$. The noise term $\epsilon$ is assumed to follow a multivariate Gaussian distribution with mean zero and covariance $\sigma_\epsilon^2I_N$. The key difference from traditional factor analysis is the choice of $\chi$ as a valid eigenvector matrix for a graph laplacian. Finding a maximum a posterior estimate of $h$ reduces to solving the optimization problem

@@

<hr />
\begin{align*}
&\textbf{Algorithm 1: Binary Signal Graph Learning} \\
&1) \textbf{ Input: } \text{ Input binary signals on a graph } \mathbf{Y}.\\
&2) \textbf{ Output: } \text{ Output an estimated } \mathbf{A}.\\
&3) \textbf{ Initialization: } h_{i,0} \sim \mathcal{U}(-1,1) \text{ for } i = 1,\ldots, N \\
&4) \textbf{ for } t = 1, \ldots, iter:\\
&5) \textbf{ Update } \mathbf{A} \textbf{ given } h:\\
&6) \,\,\,\, \textit{ Fix }  h \textit{ in Optimization Program and solve } \mathbf{A} \\
&7) \textbf{        Update } h \textbf{ given } \mathbf{A}:\\
&8) \,\,\,\, \textit{ Fix } \mathbf{A} \text{ in Optimization Program and solve h} \\
&9) \textbf{ end for }
\end{align*}
<hr />

@@

This work is supported by Research, Scholarship, and Creative Activity (RSCA) Award 2021-2022 through Chico State Enterprises. Thank you to Dr. Robin Donatello, Ph.D., for approving this work for Data Science Capstone Project

@@

# Reference {-}
